
## The present study 

The present study sought to further our understanding of dominance, prestige, and leadership motivations in human decision-making. Furthering this, we seek to bridge the connection between risk-taking behaviors, from diverse domains, and the dominance, prestige, and leadership orientations. Following the literature, we predicted that participants that were high in dominance orientation would be more likely to not only engage in risky behaviors but praise the benefits of participating in those behaviors. Individuals with prestige or leadership orientation.

## Experiment 1

## Methods

Participants were a convenience sample of `r printnum(nrow(experiment_1_Dataset))` individuals from Prolific Academic's crowdsourcing platform (www.prolific.io). Prolific Academic is an online crowdsourcing service that provides participants access to studies hosted on third-party websites. Participants were required to be 18 years of age or older and be able to read and understand English. Participants received £4.00, which is above the current minimum wage pro-rata in the United Kingdom, as compensation for completing the survey. The Psychology Research Ethics Committee at the University of Edinburgh approved all study procedures [ref: 212-2021/1]. The present study was pre-registered along with a copy of anonymized data along with a copy of the R code and supplemental materials are available at ([https://osf.io/s4j7y](https://osf.io/s4j7y)).

```{r demographicTableExperiment1}
demo_table <- experiment_dataset_analysis %>%
    mutate_at(vars(locfunc(experiment_dataset_analysis, "Gender")), ~ as.factor(recode(., "0" = "Female", "1" = "Male")))
demo_table_1 <- demo_table %>%
    select(Age, Gender, Ethnicity, Education) %>%
    tbl_summary(type = list(Age ~ "continuous2"), digits = list(Age ~ c(0, 2)), statistic = all_continuous() ~ c("{mean} ({sd})", "{median} [{min}, {max}]"), missing = "no")
mod_df_exp1 <- na.omit(as.data.frame(gtsummary::as_tibble(demo_table_1)))

apa_table(mod_df_exp1, row.names = FALSE, placement = "ht", stub_indents = list("Age" = c(1:2), "Gender" = c(3:4), "Ethnicity" = c(5:11), "Education" = c(12:18)), col.names = c("Characteristic", "N=109"), caption = "Experiment 1: Participant Demographics")
```

## Materials

\newpage

### *Demographic Questionnaire*

In a demographic questionnaire administered prior to the main survey, participants were invited to respond to a series of questions about their self-identified demographic characteristics such as age, gender, ethnicity, and ethnic origin.

### *Dominance, Prestige, and Leadership Orientation*

The 18-item Dominance, Prestige, and Leadership scale, DoPL [@suessenbach2019], is used to measure dominance, prestige, and leadership orientation. Each question corresponds to one of the three domains. Each domain is scored across six unique items related to those domains (e.g., "I relish opportunities in which I can lead others" for leadership) and rated on a scale from 0 (Strongly disagree) to 5 (Strongly agree). Included in this scale are 15 masking questions obtained from the unified motives scale [@schonbrodt2012] consistency reliability for the current sample is $\alpha$ = `r psych::alpha(experiment_1_Dataset[,DoPLQuestions])$total$std.alpha`. 

### *Domain Specific Risk-taking Scale*

The 40-item Domain-Specific Risk-taking Scale, DOSPERT [@weber2002] is a scale assessing individuals' likelihood of engaging in risky behaviors within 5 domain-specific risky situations: financial ("Gambling a week's income at a casino."), social ("Admitting that your tastes are different from those of your friends"), recreational ("Trying out bungee jumping at least once"), health and safety ("Engaging in unprotected sex"), and ethical ("Cheating on an exam") situations. Each risky situation is then rated on a five-point Likert scale (1 being very unlikely and 5 being very likely). Two additional five-point Likert scales assess risk perception and expected benefits (1 being not at all risky and 5 being extremely risky; 1 being no benefits at all and 5 being great benefits) respectively. Example risky situations are "Admitting that your tastes are different from those of a friend" and "Drinking heavily at a social function." Internal consistency reliability for the current samples for the 3 sub-domains are $\alpha$ = `r psych::alpha(experiment_1_Dataset[,riskQuestions], check.keys = TRUE)$total$std.alpha`, $\alpha$ = `r psych::alpha(experiment_1_Dataset[,riskPerceptionQuestions], check.keys = TRUE)$total$std.alpha`, $\alpha$ = `r psych::alpha(experiment_1_Dataset[,riskBenefitQuestions], check.keys = TRUE)$total$std.alpha` respectively. 

## Procedure

Participants were recruited via a study landing page on Prolific's website or via a direct e-mail to eligible participants [@prolificacademic2018]. The study landing page included a brief description of the study including any risks and benefits along with expected compensation for successful completion. Participants accepted participation in the experiment and were directed to the main survey (Qualtrics, Inc; Provo, UT) where they were shown a brief message on study consent.

Once participants consented to participate in the experiment they answered a series of demographic questions. Once completed, participants completed the Dominance, Prestige, and Leadership Scale and the Domain Specific Risk-taking scale. The two scales were counterbalanced to account for order effects. After completion of the main survey, participants were shown a debriefing statement that briefly mentions the purpose of the experiment along with the contact information of the main researcher (AI). Participants were compensated £4.00 via Prolific Academic.

## Data analysis

Demographic characteristics were analyzed using multiple regression for continuous variables (age) and Chi-square tests for categorical variables (gender, race, ethnicity, ethnic origin, and education). Means and standard deviations were calculated for the relevant scales (i.e., DoPL and DOSPERT). All analyses were done using [@rcoreteam2021] along with the [@burkner2017] package.

The use of bayesian statistics has a multitude of benefits to statistical analysis and research design. One important benefit is the use of prior data in future analyses. Termed as priors, is the use of prior distributions for future analysis. This allows for the separation of how the data might have been collected or what the intention was. In essence, the data is the data without the interpretation of the scientist. 

All relevant analyses were conducted in a Bayesian framework using the brms package [@burkner2018] along with the cmdstanr packages notes [@gabry2021]. In addition to the aforementioned packages, we used bayestestR, rstan, and papaja [@makowski2019; @aust2020; @standevelopmentteam2020]. 


## Results

One hundred and eleven individuals completed the main survey. Of these individuals, 111 completed all sections without incomplete data and were therefore retained in most data analyses. In later analyses to account for outliers, two participants had to be excluded from the dataset. Table 1 shows the demographic information for the participants. The average completion time for participants was 20M 58s (*SD* = 10M 43s). 

### Preregistered Analyses

We first investigated DoPL orientation on general risk preference (Figure \@ref(fig:DoPL-Experiment-1)). General risk preference was anecdotally explained by dominance orientation, participant gender, and participant age (see table \@ref(tab:demographicTableExperiment1)). General distributions of dominance, prestige, and leadership then warranted further analysis. To investigate the interaction of power orientation and DOSPERT we followed the methods described in the DOSPERT scoring manual found on the official DOSPERT Scale website ([DOSPERT Scoring Instructions](https://sites.google.com/a/decisionsciences.columbia.edu/dospert/scoring-instructions)). This involves calculating the alpha and beta coefficients and then from there calculating the overall preferences for each of the subdomains and the overall domains for general risk preference along with the perception and benefit preferences for risk. 

#### *Demographic and DoPL*

All participants completed the dominance, leadership, and prestige scale [@suessenbach2019]. Empirically, men have generally been more dominance-oriented in their behavior [@rosenthal2012].Following the literature as well, dominant men tended to prefer risk more so  than women (95% CI b = `r printnum(m1_int_fixef_exp_1_j["Gender", "Estimate"])`,[`r paste0(m1_int_fixef_exp_1_j["Gender", c("CI Low", "CI High")], collapse = ", ")`]). The marginal posterior distribution of each parameter is summarized in Table 1. Interestingly, older individuals tended to be more dominance-oriented than younger individuals. 

#### General Risk and DoPL

Further investigations, as previously mentioned investigated DoPL's interactions with general risk preference. As stated, domianance appears to be the strongest predictor of general risk preference (95% CI b = `r printnum(m1_int_fixef_exp_1_j["Dominance", "Estimate"])`, [`r paste(m1_int_fixef_exp_1_j["Dominance", c("CI Low", "CI High")], collapse = ", ")`]). Overall, younger individuals tended to have a stronger preference for risk (95% CI b = `r printnum(m1_int_fixef_exp_1_j["Age", "Estimate"])`, [`r paste(m1_int_fixef_exp_1_j["Age", c("CI Low", "CI High")], collapse = ", ")`]). Those that tended to be lower in leadership orientation had a tendency to be generally more risk averse than their counterparts (95% CI b = `r printnum(m1_int_fixef_exp_1_j["Leadership", "Estimate"])`, [`r paste(m1_int_fixef_exp_1_j["Leadership", c("CI Low", "CI High")], collapse = ", ")`]). 

### Domain-Specific Risk-Taking

As predicted individuals that identified as male were more likely to endorse risk-taking behaviors, namely ethical, social, financial, and recreational domains (see \@ref(fig:DoPL-Experiment-1)). 

### Interactions  

When investigating dominance, prestige, and leadership motivations with domain-specific risk-taking findings supported the common expectations in the literature. Table 5 shows the interactions with like CI values. Dominance overall explained the relationship between DoPL orientation and preference, specifically (95% CI b = `r printnum(m3_int_fixef_exp_1["Ethical Preference * Dominance", "Estimate"])`, [`r paste(m3_int_fixef_exp_1["Ethical Preference * Dominance", c("CI Low", "CI High")], collapse = ", ")`], financial, b = `r printnum(m3_int_fixef_exp_1["Financial Preference * Dominance", "Estimate"])`, [`r paste(m3_int_fixef_exp_1["Financial Preference * Dominance", c("CI Low", "CI High")], collapse = ", ")`], social, b = `r printnum(m3_int_fixef_exp_1["Social Preference * Dominance", "Estimate"])`, [`r paste(m3_int_fixef_exp_1["Social Preference * Dominance", c("CI Low", "CI High")], collapse = ", ")`], health and safety, b = `r printnum(m3_int_fixef_exp_1["Health and Safety Preference * Dominance", "Estimate"])`, [`r paste(m3_int_fixef_exp_1["Health and Safety Preference * Dominance", c("CI Low", "CI High")], collapse = ", ")`], and recreational, b = `r printnum(m3_int_fixef_exp_1["Recreational Preference * Dominance", "Estimate"])`, [`r paste(m3_int_fixef_exp_1["Recreational Preference * Dominance", c("CI Low", "CI High")], collapse = ",")`]) respectively. Full interactions can be found in table 4. Participant age and gender also appeared to affect recreational preference (95% CI b = `r printnum(m3_int_fixef_exp_1["Recreational Preference * Gender", "Estimate"])`, [`r paste(m3_int_fixef_exp_1["Recreational Preference * Gender", c("CI Low", "CI High")], collapse = ", ")`], b = `r printnum(m3_int_fixef_exp_1["Recreational Preference * Age", "Estimate"])`, [`r paste(m3_int_fixef_exp_1["Recreational Preference * Age", c("CI Low", "CI High")], collapse = ", ")`]) respectively.

Following these findings, we investigated the effect of DoPL on general risk preference and found that dominance overall predicted risk preference along with gender and age of the participant (Table \@ref(tab:m1-fixef-Experiment-1)). 

### DOSPERT Sub-categorizations

Risk preferences is generally made up of benefits and perceptions of risk. Outside of perceptions and benefits, dominance and males who are dominance oriented were the strongest predictors of likelihood in engaging in a risky situation (95% CI b = `r printnum(m5_int_fixef_exp_1["Risk * Dominance", "Estimate"])`, [`r paste(m5_int_fixef_exp_1["Risk * Dominance", c("CI Low", "CI High")], collapse = ", ")`] and b = `r printnum(m5_int_fixef_exp_1["Risk * Dominance : Gender", "Estimate"])`, [`r paste(m5_int_fixef_exp_1["Risk * Dominance : Gender", c("CI Low", "CI High")], collapse = ", ")`]). Dominance also appeared to be a strong predictor of perceiving more benefits of engaging in a risky situation (95% CI b = `r printnum(m5_int_fixef_exp_1["Risk Benefit * Dominance", "Estimate"])`, [`r paste(m5_int_fixef_exp_1["Risk Benefit * Dominance", c("CI Low", "CI High")], collapse = ", ")`]) along with gender where males are more likely to perceive benefits (95% CI b = `r printnum(m5_int_fixef_exp_1["Risk Benefit * Gender", "Estimate"])`, [`r paste(m5_int_fixef_exp_1["Risk Benefit * Gender", c("CI Low", "CI High")], collapse = ", ")`]).

Alternatiively, prestige appeared to be a stronger predictor of perceiving risks than others along with female participants and female participants that are higher in leadership orientation (95% CI b = `r printnum(m5_int_fixef_exp_1["Risk Perception * Prestige", "Estimate"])`, [`r paste(m5_int_fixef_exp_1["Risk Perception * Prestige", c("CI Low", "CI High")], collapse = ", ")`], b = `r printnum(m5_int_fixef_exp_1["Risk Perception * Gender", "Estimate"])`, [`r paste(m5_int_fixef_exp_1["Risk Perception * Gender", c("CI Low", "CI High")], collapse = ", ")`], and b = `r printnum(m5_int_fixef_exp_1["Risk Perception * Leadership : Gender", "Estimate"])`, [`r paste(m5_int_fixef_exp_1["Risk Perception * Leadership : Gender" , c("CI Low", "CI High")], collapse = ", ")`]). Full predictors can be seen in table \@ref(tab:m5-int-fixef-exp-1). 

### Discussion and limitations

\newpage

# Experiment 2

## The present experiment

Experiment 1 was ran to understand how risk and decision-making interplay using the aforementioned materials. Following this we found, as predicted, individuals that are higher in dominance orientation are more likely to engage in risky behaviors. Namely financial, social, and health and safety risks (see the above for more precise findings). From here we wanted to further investigate risk behaviors and power motives to see if dominance orientation is a stronger predictor of risk-taking behaviors than say for example pathological narcissism, which is often part of the discussion of risk behaviors [@buelow2014; @foster2009; @leder2021]. In doing so we intend to see, along with a mediation analysis approach, if dominance again will not just be the strongest predictor of risk-taking behaviors, but also the strongest mediator as well compared to pathological narcissism. Through this we hope to better understand how individuals make decisions in risky situations along with creating theories surrounding risky situations before the decisions have been made.

## Methods

Materials remain the same in terms of the (1) Demographic Questionnaire, (2) Dominance, Prestige, and Leadership Questionnaire, and (3) DOSPERT Questionnaire. However, we added the Brief-Pathological Narcissism Inventory to assess possible interactions of dominance and narcissism in risky decision-making. 

## Participants

Following experiment 1, participants were a convenience sample of `r nrow(Experiment_2_demographic_dataset)` individuals from Prolific Academic's crowdsourcing platform (www.prolific.io). Prolific Academic is an online crowdsourcing service that provides participants access to studies hosted on third-party websites. Participants were required to be 18 years of age or older and be able to read and understand English. In addition, similar to participant demographics in experiment 1, participants were majority white along with having a university undergraduate degree. Participants received £3.00, which is above the current minimum wage pro-rata in the United Kingdom, as compensation for completing the survey. The Psychology Research Ethics Committee at the University of Edinburgh approved all study procedures [ref: 212-2021/2]. The present study was pre-registered along with a copy of anonymized data and a copy of the R code is available at ([https://osf.io/s4j7y](https://osf.io/s4j7y)).

```{r demographicTableExperiment2}
df_exp_2 <- d2 %>%
    select(Age, Gender, Ethnicity, Education, Ethnic_Origin) %>%
    tbl_summary(type = list(Age ~ "continuous2"), digits = list(Age ~ c(0, 2)), statistic = all_continuous() ~ c("{mean} ({sd})", "{median} [{min}, {max}]"), missing = "no")
mod_df <- na.omit(as.data.frame(gtsummary::as_tibble(df_exp_2)))

apa_table(mod_df, row.names = FALSE, stub_indents = list("Age" = c(1:2), "Gender" = c(3:6), "Ethnicity" = c(7:12), "Education" = c(13:19), "Ethnic Origin" = c(20:25)), escape = F, col.names = c("Characteristic", "N=279"), caption = "Experiment 2: Participant Demographics")
```

## Materials

### *Brief-Pathological Narcissism Inventory* 

The 28-item Brief Pathological Narcissism Inventory (B-PNI; @schoenleber2015) is a modified scale of the original 52-item Pathological Narcissism Inventory (PNI; @pincus2009). Like the PNI, the B-PNI is a scale measuring individuals' pathological narcissism. Items in the B-PNI retained all 7 pathological narcissism facets from the original PNI (e.g., exploitativeness, self-sacrificing self-enhancement, grandiose fantasy, contingent self-esteem, hiding the self, devaluing, and entitlement rage). Each item is rated on a 5-point Likert scale ranging from 1 (not at all like me) to 5 (very much like me). Example items include "I find it easy to manipulate people" and "I can read people like a book." B-PNI was well correlated within itself `r psych::alpha(Experiment_2_dataset_raw[,PNI_Questions])$total$std.alpha` along with strong internal consistency within the sub-domains of pathological narcissism, i.e., $/alpha$'s for Grandiosity (`r psych::alpha(Experiment_2_dataset_raw[,Grandiosity_Questions])$total$std.alpha`) and Vulnerability (`r psych::alpha(Experiment_2_dataset_raw[,Vulnerability_Questions])$total$std.alpha`). 

## Procedure

Participants were recruited via a study landing page on Prolific's website or via a direct e-mail to eligible participants [@prolificacademic2018]. The study landing page included a brief description of the study including any risks and benefits along with expected compensation for successful completion. Participants accepted participation in the experiment and were directed to the main survey on pavlovia.org (an online JavaScript hosting website similar to Qualtrics) where they were shown a brief message on study consent.

Once participants consented to participate in the experiment they answered a series of demographic questions. Once completed, participants completed the Dominance, Prestige, and Leadership Scale and the Domain Specific Risk-taking scale. An additional survey was added (the novel aspect of experiment 2) where participants, in addition to the two previous surveys, were asked to complete the brief-pathological narcissism inventory. The three scales were counterbalanced to account for order effects. After completion of the main survey, participants were shown a debriefing statement that briefly mentions the purpose of the experiment along with the contact information of the main researcher (AI). Participants were compensated £3.00 via Prolific Academic. 

## Data analysis

Demographic characteristics were analyzed using multiple regression for continuous variables (age) and Chi-square tests for categorical variables (gender, race, ethnicity, ethnic origin, and education). Means and standard deviations were calculated for the relevant scales (i.e., DoPL and DOSPERT). All analyses were done using [@rcoreteam2021] along with the [@burkner2017] package.

The use of bayesian statistics has a multitude of benefits to statistical analysis and research design. One important benefit is the use of prior data in future analyses. Termed as priors, is the use of prior distributions for future analysis. This allows for the separation of how the data might have been collected or what the intention was. In essence, the data is the data without the interpretation of the scientist. 

All relevant analyses were conducted in a Bayesian framework using the brms package [@burkner2018] along with the cmdstanr packages notes [@gabry2021]. In addition to the aforementioned packages, we used bayestestR, rstan, and papaja for analysis along with the creation of this manuscript [@makowski2019; @aust2020; @standevelopmentteam2020].

## Results and Discussion

`r english::Words(nrow(Experiment_2_dataset_raw))` individuals participated in the present experiment. Of those 54% identified as male (*n* = 155). Table 3 shows the demographic information for Experiment 2. Furthering, table 4 illustrates a Bayesian correlational matrix of all the measures wherein content-based similar measures illustrated positive and negative correlations consistent with expectations. The average completion time for participants was `r paste(round(seconds_to_period(rowMeans(Experiment_2_timing[nrow(Experiment_2_timing),])), 2))` (*SD* = `r paste(round(seconds_to_period(sd(Experiment_2_timing[nrow(Experiment_2_timing),])), 2))`)

In general, male participants were more likely to endorse dominance-oriented statements, (95% CI b = `r printnum(m3_fixef_exp_2_j["Dominance * Gender", "Estimate"])`, [`r paste(m3_fixef_exp_2_j["Dominance * Gender",c("CI Low", "CI High")], collapse = ", ")`]). Along with younger indvidiuals tending to also endorse dominant-oriented statements, (95% CI b = `r printnum(m3_fixef_exp_2_j["Dominance * Age", "Estimate"])`, [`r paste(m3_fixef_exp_2_j["Dominance * Age", c("CI Low", "CI High")], collapse = ", ")`]). 

### Preregistered Analyses

#### Dominance

Following the previous basic results, we began our pre-regisetered analysis found in the pre-registration found on OSF.io. Dominance-oriented indvidiual was a strong predictor of multiple domains of risk-taking. Namely, participants that have a preference for both financial and social risk-taking, (95% CI b = `r printnum(m3_interaction_gender_fixef_exp_2["Financial Preference * Dominance", "Estimate"])`, [`r paste(m3_interaction_gender_fixef_exp_2["Financial Preference * Dominance", c("CI Low", "CI High")], collapse = ", ")`]) and (95% CI b = `r printnum(m3_interaction_gender_fixef_exp_2["Social Preference * Dominance", "Estimate"])`, [`r paste(m3_interaction_gender_fixef_exp_2["Social Preference * Dominance", c("CI Low", "CI High")], collapse = ", ")`]) respectively. Investigating gender differences and found that males with a preference for financial risk-taking were more likely to endorse dominant-oriented statements, (95% CI b = `r printnum(m3_interaction_gender_fixef_exp_2["Financial Preference * Dominance : Gender", "Estimate"])`, [`r paste(m3_interaction_gender_fixef_exp_2["Financial Preference * Dominance : Gender", c("CI Low", "CI High")], collapse = ", ")`]).

#### Prestige 

Differentiating between DoPL domains, males with a preference for social risk-taking were more likely to endorse prestige-oriented statements along with indivdiuals with a general preference for social risk-taking, (95% CI b = `r printnum(m3_interaction_gender_fixef_exp_2["Social Preference * Prestige : Gender", "Estimate"])`, [`r paste(m3_interaction_gender_fixef_exp_2["Social Preference * Prestige : Gender", c("CI Low", "CI High")], collapse = ", ")`]) and (95% CI b = `r printnum(m3_interaction_gender_fixef_exp_2["Social Preference * Prestige", "Estimate"])`, [`r paste(m3_interaction_gender_fixef_exp_2["Social Preference * Prestige", c("CI Low", "CI High")], collapse = ", ")`]) respectively. 

#### Leadership

Finally, leadership orientation follows a similar trend seen with dominance and prestige orientations. Males with a preference for social risk-taking were more likely to endorse leadership-oriented statements along with individuals with a less of a preference for recreational risk-taking endorsing leadership-oriented statements , (95% CI b = `r printnum(m3_interaction_gender_fixef_exp_2["Social Preference * Leadership : Gender", "Estimate"])`, [`r paste(m3_interaction_gender_fixef_exp_2["Social Preference * Leadership : Gender", c("CI Low", "CI High")], collapse = ", ")`]) and (95% CI b = `r printnum(m3_interaction_gender_fixef_exp_2["Recreational Preference * Leadership", "Estimate"])`, [`r paste(m3_interaction_gender_fixef_exp_2["Recreational Preference * Leadership", c("CI Low", "CI High")], collapse = ", ")`]) respectively.

### Brief-Pathological Narcissism Inventory

We furthered our analyses, as seen in the pre-registration found on OSF.io by investigating pathological narcissism and its components through the Brief-Pathological Narcissism Inventory (B-PNI). Preliminary investigations of pathological narcissism in our sample show that younger individuals on average tended to present more narcissistic opinions (95% CI b = `r printnum(pni_model_dopl_fixef_exp_2_j["Age", "Estimate"])`, [`r paste(pni_model_dopl_fixef_exp_2_j["Age", c("CI Low", "CI High")], collapse = ", ")`]). The B-PNI further differentiates between grandiose and vulnerability. Interestingly, women tended to present more vulnerable narcissism traits than men (95% CI b = `r printnum(pni_multi_dopl_fixef_exp_2_j["Vulnerability * Gender", "Estimate"])`, [`r paste(pni_multi_dopl_fixef_exp_2_j["Vulnerability * Gender", c("CI Low", "CI High")], collapse = ", ")`]). Younger individuals tended to present more grandiose narcissism traits (95% CI b = `r printnum(pni_multi_dopl_fixef_exp_2_j["Grandiosity * Age", "Estimate"])`, [`r paste(pni_multi_dopl_fixef_exp_2_j["Grandiosity * Age", c("CI Low", "CI High")], collapse = ", ")`]). This same tendency for younger individuals was seen with vulnerable narcissism traits (95% CI b = `r printnum(pni_multi_dopl_fixef_exp_2_j["Vulnerability * Age", "Estimate"])`, [`r paste(pni_multi_dopl_fixef_exp_2_j["Vulnerability * Age", c("CI Low", "CI High")], collapse = ", ")`]).

Grandiose narcissism is then separated further into grandiose fantasy, exploitativeness, and self-sacrificing and self-enhancement. Selected findings are males tend to demonstrate more exploitativeness and younger individuals tended to present more exploitative and grandiose narcissism (95% CI b = `r printnum(multi_model_dospert_fixef_exp_2_j["Exploitativeness * Age", "Estimate"])`, [`r paste(multi_model_dospert_fixef_exp_2_j["Exploitativeness * Age", c("CI Low", "CI High")], collapse = ", ")`]) and (95% CI b = `r printnum(multi_model_dospert_fixef_exp_2_j["Grandiose Fantasy * Age", "Estimate"])`, [`r paste(multi_model_dospert_fixef_exp_2_j["Grandiose Fantasy * Age", c("CI Low", "CI High")], collapse = ", ")`]) respectively. Further analysis is shown in table \@ref(tab:vulnerabiliotyGrandiosityAndGenderExperiment2). 

Vulnerable narcissism, like grandiose narcissism, is separated further into contingent self-esteem, devaluing, entitlement rage, and hiding the self. Financial preference appears to be overall the best DOSPERT predictor of vulnerable narcissism sub-domains specifically for contingent self-esteem (95% CI b = `r printnum(multi_2_model_dospert_int_fixef_exp_2_j["Contingent Self-Esteem * Financial Preference", "Estimate"])`, [`r paste(multi_2_model_dospert_int_fixef_exp_2_j["Contingent Self-Esteem * Financial Preference", c("CI Low", "CI High")], collapse = ", ")`]), devaluing Men (95% CI b = `r printnum(multi_2_model_dospert_int_fixef_exp_2_j["Devaluing * Financial Preference : Gender", "Estimate"])`, [`r paste(multi_2_model_dospert_int_fixef_exp_2_j["Devaluing * Financial Preference : Gender", c("CI Low", "CI High")], collapse = ", ")`]), and hiding the self (95% CI b = `r printnum(multi_2_model_dospert_int_fixef_exp_2_j["Hiding the Self * Financial Preference", "Estimate"])`, [`r paste(multi_2_model_dospert_int_fixef_exp_2_j["Hiding the Self * Financial Preference", c("CI Low", "CI High")], collapse = ", ")`]). 

### Risk and interactions 

Overall, anecdotally dominance appears to explain the overall individual perceptions, benefits, and likelihood of risk judgments (95% CI b = `r printnum(pni_risk_dospert_fixef_exp_2_j["Risk Perception * Dominance", "Estimate"])`, [`r paste(pni_risk_dospert_fixef_exp_2_j["Risk Perception * Dominance", c("CI Low", "CI High")], collapse = ", ")`]), (95% CI b = `r printnum(pni_risk_dospert_fixef_exp_2_j["Risk Benefit * Dominance", "Estimate"])`, [`r paste(pni_risk_dospert_fixef_exp_2_j["Risk Benefit * Dominance", c("CI Low", "CI High")], collapse = ", ")`]), and (95% CI b = `r printnum(pni_risk_dospert_fixef_exp_2_j["Risk * Dominance", "Estimate"])`, [`r paste(pni_risk_dospert_fixef_exp_2_j["Risk * Dominance", c("CI Low", "CI High")], collapse = ", ")`]) respectively. Similarly, when looking at further sub-categorizations of general risk preferences there does appear to be mainly a bias with regards to age, where younger individuals overall have a higher risk preference than their older counterparts.

### Domain-Specific Risk-Taking

Looking at Domain Specific Risk-taking, we analyzed DOSPERT similarly to previous analyses. Overall, domain-specific risk-taking was explained by dominance orientation along with prestige and leadership. Interesting interactions were present with individual domains for narcissism as well.

Overall, age was an effective predictor for both grandiose and vulnerable narcissism with younger indivdiuals tending towards being more narcissitic for both grandiose and vulnerable traits (95% CI b = `r printnum(pni_multi_dospert_int_fixef_exp_2_j["Grandiosity * Age", "Estimate"])`, [`r paste(pni_multi_dospert_int_fixef_exp_2_j["Grandiosity * Age", c("CI Low", "CI High")], collapse = ", ")`]), and (95% CI b = `r printnum(pni_multi_dospert_int_fixef_exp_2_j["Vulnerability * Age", "Estimate"])`, [`r paste(pni_multi_dospert_int_fixef_exp_2_j["Vulnerability * Age", c("CI Low", "CI High")], collapse = ", ")`]) respecitively. Preferences for financial and males with a recreational risk preference tended to express more vulnerable narcissism traits (95% CI b = `r printnum(pni_multi_dospert_int_fixef_exp_2_j["Vulnerability * Financial Preference", "Estimate"])`, [`r paste(pni_multi_dospert_int_fixef_exp_2_j["Vulnerability * Financial Preference", c("CI Low", "CI High")], collapse = ",")`]) and (95% CI b = `r printnum(pni_multi_dospert_int_fixef_exp_2_j["Vulnerability * Gender", "Estimate"])`, [`r paste(pni_multi_dospert_int_fixef_exp_2_j["Vulnerability * Gender", c("CI Low", "CI High")], collapse = ", ")`]) respectively.

### Interactions

Following traditional Bayesian models, we analyzed relationships through a Bayesian mediation model using the brms Bayesian structural equation modeling software along with it's software to create a multilevel model [@burkner2017; @burkner2018]. Centralized in the model is risk preference. In this exploratory model we were investigating to see what is the best predictor variable is the best mediatior in our analysis. Figure \@ref(fig:Experiment2ModelSEM) respresents our hypothetical model of dominance being the strongest mediator. 

```{r mediationComparisonExp2}
apa_table(mediation_comparison_exp_2, caption = "Experiment 2 | Mediation model comparison", note = "Bayesian Comparison between 4 models investigating the differences of 4 different variables as mediators.")
```

In this model, we constructed multilevel equations where we focused on different variables being the strongest mediator. Then using the brms Baysian r package, we then compared the models to see which mediator was indeed the strongest mediator. How hypothesis where dominance would be the strongest mediator was accepted, model 2 as shown in table \@ref(tab:mediationComparisonExp2). 




# General Discussion and Implications


